### 2016-02-22 paper.tex
Discuss solidity range

The rotor was 1.075 m in diameter and 0.8067 m tall, with blade chords that
taper from 0.04 m at the tips to 0.067 m at the roots, or half-span. Mean
chord-to-radius ratio $c/R$ was 0.1, which is approximately at the threshold
between high and low solidity \cite{Strickland1981,Fiedler2009}. This rotor
geometry presents a unique validation case not yet seen in the literature,
similar in concept to the VAWT 850 \cite{Mays1990} with its tapered blades, but
with a moderately high $c/R$ to more accurately represent typical MHK rotors,
which presents a challenge for numerical modeling.

>>>>

The rotor was 1.075 m in diameter and 0.8067 m tall, with blade chords that
taper from 0.04 m at the tips to 0.067 m at the roots, or half-span, varying the
chord-to-radius ratio $c/R$ from 0.07 to 0.12 (0.1 average). The rotor was
therefore approximately at the threshold between high and low solidity
\cite{Strickland1981,Fiedler2009}, which presents a unique validation case not
yet seen in the literature, similar in concept to the VAWT 850 \cite{Mays1990}
with its tapered blades, but with a moderately high $c/R$ to more accurately
represent typical MHK rotors, which presents a challenge for numerical modeling.
